Case study validations of automatic bullet matching

### 2018-11-26 index.Rmd
Fixing draft options?

blinded: 1 # to produce blinded version set to 1
titlepage: 0 # This gets changed automatically when the title page is compiled in the chunk child-doc-compile
draft: 0 # Set to 1 if figures should be included with the text

>>>>

# to produce blinded version set to 1
blinded: 1
# This gets changed automatically when the title page is compiled in the chunk child-doc-compile
titlepage: 0
# Set to 1 if figures should be included with the text
draft: 1
